\section{Functional and Workflows Description}
% ESO-037611 expects a section called "Functional and Workflows Description" in the DRLD
% "Data Processing Overview" is the term used for the DRLS.
%\section{Data Processing Overview}
\label{sec:data_processing_overview}

The METIS data reduction system runs in different environments and
serves various purposes.  According to the setting, the following
pipeline levels are distinguished~\cite{1618}:

\begin{description}
\item[Quality Control Level 0 (QC0):] The QC0 pipeline runs
  automatically in real time on a dedicated pipeline workstation in
  the instrument control room at the observatory. Its purpose is to
  analyse every FITS file created by the instrument and produce
  quality control parameters that allow assessment of whether the
  observation and instrument performance were within specifications.
  The appropriate reduction recipe is triggered either when a single
  FITS file is delivered to the workstation or when a template is
  finished. The files are classified based on header keywords, grouped
  and associated to the necessary standard calibration files.

\item[Quality Control Level 1 (QC1):] The goal of the QC1 pipeline is
  to produce certified calibration products from calibration
  observations as well as to produce QC parameters that are used to
  check the quality of observations and to monitor observing
  conditions and instrument health.
  The QC1 pipeline is run automatically by ESO in Garching.
  Calibration products and QC parameters are ingested into the ESO Science Archive.

\item[Quality Control Level 2 (QC2):] The QC2 pipeline produces
  Science Data Products compliant with~\cite{ESO-products_standard} as
  well as QC parameters derived from science exposures. It runs
  offline in an automatic way and uses the best calibration products
  for the night of observation (produced by the QC1 pipeline).
  The QC2 pipeline is run automatically by ESO in Garching.
  Science data products and QC parameters are ingested into the ESO Science Archive.

\item[Science-Grade Desktop Environment:] The pipeline recipes are
  delivered to the astronomical community to enable users to reduce
  data in an optimal and interactive way. Recipes can be run from the
  command line using the \lstinline{esorex} front-end or in the
  context of a \lstinline{Reflex}/\ac{EDPS} workflow. While the desktop recipes
  are identical to those used in the QC2 pipeline, the user can change
  recipe parameters to optimise the reduction. Within the
  \lstinline{Reflex}/\ac{EDPS} environment, interactive tools are provided that
  allow the user to assess the quality of individual reduction steps
  and to repeat them with different parameters. The products of this
  pipeline are compliant with~\cite{ESO-products_standard}.

\end{description}


The rest of this document describes the recipes primarily from the perspective of the desktop pipeline.
The QC0, QC1, QC2 pipelines use the subset of these recipes necessary for the goals described above.
Recipes used in the QC0 environment are written such that they can be run in real time, possibly requiring different defaults for processing parameters.


\subsection{Required calibrations}
\label{ssec:calibrations}

Table~\ref{tab:calibrations_per_mode} (taken from
\cite{METIS-calibration_plan}) lists the main calibration steps that
are required for each instrument mode.

%\TODO{Do we apply NCPA + PSF to HCI data? For ADI a simple recipe is foreseen.} The NCPA estimating algorithms are still under study by the HCI team.
%\begin{landscape}
\begin{table}
  \newcommand{\yes}{\tikz\fill[scale=0.35,color=green!50!black](0,.35) -- (.25,0) -- (0.9,.7) -- (.25,.15) -- cycle;}
  \newcommand{\no}{\textcolor{red!50!black}{---}}
    \caption[Overview of required calibrations per instrument mode]{Overview of required calibrations per instrument mode.
    The IFU modes refer to both the nominal configuration and to the extended wavelength configuration. From~\cite{METIS-calibration_plan}.}
  \label{tab:calibrations_per_mode}
  \centering\scriptsize
  \begin{tabularx}{\textwidth}{lXccXccccc}
    \hline
                           & Dark / Linearity & Flat & Wave & Offset type & Telluric & Flux & Distortion & NCPA + PSF & RSRF \\
    \hline\hline
    \CODE{IMG_LM}          & \yes & \yes & \no  & Dither         & \no      & \yes & \yes       & \no        & \no  \\
    \CODE{IMG_LM_(RA/C)VC} & \yes & \yes & \no  & ADI            & \no      & \yes & \yes       & \yes       & \no  \\
 %   \CODE{IMG_LM_CLC}      & \yes & \yes & \no  & ADI            & \no      & \yes & \yes       & \yes       & \no  \\
    \CODE{IMG_LM_APP}      & \yes & \yes & \no  & Dither + ADI   & \no      & \yes & \yes       & \yes       & \no  \\
    \CODE{SPEC_LM}         & \yes & \no  & \yes & Dither along slit & \yes  & \yes & \yes       & \no        & \yes \\
    \CODE{IFU}             & \yes & \no  & \yes & Dither         & \yes     & \yes & \yes       & \no        & \yes \\
    \CODE{IFU_APP}         & \yes & \no  & \yes & Dither\footnote{Dithering for background subtraction + IFU\_APP will not be practical due to AO halo.}  + ADI  & \yes     & \yes & \yes       & \yes       & \yes \\
    \CODE{IFU_(RA/C)VC}    & \yes  & \no  & \yes & ADI            & \yes     & \yes & \yes       & \yes       & \yes \\
   % \CODE{IFU_CLC}         & \yes & \no  & \yes & Dither + ADI   & \yes     & \yes & \yes       & \yes       & \yes \\
    \hline
    \CODE{IMG_N}           & \yes  & \yes & \no  & chop/nod       & \no      & \yes & \yes       & \no        & \no  \\
    \CODE{IMG_N_CVC}       & \yes  & \yes & \no  & three-point chopping & \no & \yes & \no       & \yes       & \no  \\
 %   \CODE{IMG_N_CLC}       & \no  & \yes & \no  & out-of-field chopping & \no & \yes & \no      & \yes       & \no  \\
    \CODE{SPEC_N_LOW}      & \yes  & \no  & \yes & chop/nod along slit & \yes & \yes & \yes      & \no        & \yes \\
    \hline
  \end{tabularx}
\end{table}
%\end{landscape}
\FloatBarrier

%%%
\input{Overview_IMG_LM_N}

%%%
\input{Overview_LSS}

%%%
\input{Overview_IFU}

\subsection{Parallel Observing Modes}
\label{ssec:combinedmodes}

There are three parallel observing modes:

\begin{itemize}
\item Parallel observing mode IMG-LM and IMG-N (Section~\ref{sssec:parallellmnimg})
\item Parallel observing mode LSS-LM and LSS-N (Section~\ref{sssec:parallellmnspec})
\item Parallel observing mode IMG-LM and IFU (Section~\ref{sssec:parallellmnspec})
\end{itemize}

The respective templates corresponding to these modes will produce raw data files that can be processed independently by the relevant workflows.
That is, the templates will trigger two different recipe cascades, and there are no specific recipes for any of the parallel observing modes.

\subsubsection{Parallel observing mode IMG-LM and IMG-N}\label{sssec:parallellmnimg}
There are two specific templates for parallel imaging observations in the LM-band and N-band:
\begin{itemize}
 \item \TPL{METIS_img_lmn_obs_AutoChopNod}
 \item \TPL{METIS_img_lmn_obs_GenericChopNod}
\end{itemize}
These templates produce two kind of raw images that are processed independently in either the LM-band or N-band imaging workflow.
This fulfills \REQ{METIS-7244}.


\subsubsection{Parallel observing mode LSS-LM and LSS-N}\label{sssec:parallellmnspec}
There is one specific template for parallel LSS observations in the LM-band and N-band:
\begin{itemize}
 \item \TPL{METIS_spec_lmn_obs_AutoChopNodOnSlit}
\end{itemize}
These templates produce two kind of raw images that are processed independently in either the LM-band or N-band LSS workflow.
This fulfills \REQ{METIS-7245}.

\subsubsection{Parallel observing mode IMG-LM and IFU}\label{sssec:parallellmifu}
Parallel observing mode IMG-LM and IFU is also needed to perform non-common path pointing and aberration correction in \ac{HCI} modes:
real-time monitoring of non-common path aberrations between the \ac{SCAO} \ac{WFS} and the \ac{HCI} elements cannot be performed with the \ac{IFU} due to slicing and sampling issues.

The IFU pickoff optic is a beamsplitter with a transmission of ~10\% to the LM imager and a reflectivity of ~90\% to the IFU. % https://polarion.astron.nl/polarion/#/project/METIS/workitem?id=METIS-3111
LM-band images can therefore be taken in parallel with the IFU exposures, for any of the IFU templates.
The LM-band images and IFU exposures are processed independently.
This fulfills \REQ{METIS-6072}.


\subsection{Workflows}
The association matrices described in the previous sections will be converted one-to-one into Reflex or \ac{EDPS} workflows.

Any interactivity in the workflows is described with the individual recipes.


\subsection{Matched FITS keywords}

The workflow management system (e.g. \ac{EDPS}) uses the `matched keywords'
to find calibration data when processing data.
That is, the system will compare the FITS keywords of the primary input, to
the FITS headers of the pool of possible calibration files to use, in order
to decide what data to use.

For example, most calibration data has to be taken with the same \FITS{DET.DIT}
and \FITS{DET.NDIT} combination as the science data.
Several calibration products also need to use the same filter, or the same mask, or the same grism as the science data.

All selections are done on equality.
That is, no interpolation between, e.g., \FITS{DET.DIT}, will be done if only an approximate matching data product is found.

The following two tables provide an overview of the matched FITS
keywords. Table~\ref{tab:fitskeywordaliasses} defines several high level keyword
aliases used for convenience when there are several combinations
of instrumental keywords (INS.) which are needed to match with the correct
calibration files. These keywords are used in the Matched Keyword
descriptions in the recipes in Chapter~\ref{sec:pipeline_recipes}.
Table~\ref{tab:fitsmatchedkeywordssummary}
summaries the input data, calibration files, and the FITS
keyworlds needed to match them for all the recipes listed in
Chapter~\ref{sec:pipeline_recipes}. The second defines various high
level aliases used for convenience when there are several combinations
of instrumental keywords which are needed to match with the correct
calibration files.

\begin{table}
    \caption{FITS keyword aliases}
    \label{tab:fitskeywordaliasses}
  \begin{tabular}[c]{|p{3cm}|p{5cm}|p{5cm}|}
      \hline
      \textbf{Alias} & \textbf{Description} & \textbf{FITS keywords} \\
      \hline
\FITS{DRS.FILTER}   & Filter Information (LM or N)  & value of \FITS{INS.OPTI10.NAME} or \FITS{INS.OPTI13.NAME} \\
\FITS{DRS.NDFILTER} & ND Filter information	        & value of \FITS{INS.OPTI11.NAME} or \FITS{INS.OPTI13.NAME} \\
\FITS{DRS.SLIT}     & Slit Information (LM or N)    & value of \FITS{INS.OPTI3.NAME} and \FITS{INS.OPTI12.NAME} or  \FITS{INS.OPTI9.NAME} \\
\FITS{DRS.MASK}     & Mask information for Coronagraphy	& value of \FITS{INS.OPTI1.NAME}, \FITS{INS.OPTI3.NAME}, \FITS{INS.OPTI5.NAME}, \FITS{INS.OPTI9.NAME}, \FITS{INS.OPTI12.NAME} \\
\FITS{DRS.PUPIL}    & Pupil information             & value of \FITS{INS.OPTI15.NAME} or \FITS{INS.OPTI16.NAME}\\
\hline
    \end{tabular}
\end{table}


\newgeometry{bottom=0.1cm, right=0.1cm, left=0.1cm, top=0.1cm}
\begin{landscape}
{
  \begin{longtable}[c]{|p{4.2cm}|p{4.6cm}|p{5.6cm}|p{3.5cm}|p{3.5cm}|}
%  \begin{longtable}[c]{|l|l|l|l|l|}
 \caption{FITS matched keywords summary}
 \label{tab:fitsmatchedkeywordssummary}
 \endfirsthead
 \hline
 \textbf{Recipe} & \textbf{Main Input} & \textbf{Calibration Data} & \textbf{FITS keywords} & \textbf{Aliases} \\
 \hline
    \endhead
 \hline
 \textbf{Recipe} & \textbf{Main Input} & \textbf{Calibration Data} & \textbf{FITS keywords} & \textbf{Aliases} \\
 \hline
\REC{metis_det_lingain} & \RAW{DETLIN_det_RAW}, \RAW{det_WCU_OFF_RAW} &  &  &  \\
\REC{metis_det_dark} & \RAW{DARK_det_RAW} & \PROD{LINEARITY_det}, \PROD{PERSISTENCE_MAP} &  &  \\
\REC{metis_det_persistence} &  &  &  &  \\
\REC{metis_lm_img_flat} & \RAW{LM_FLAT_LAMP_RAW}, \RAW{LM_FLAT_TWILIGHT_RAW} & \PROD{MASTER_DARK_2RG} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI10.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_basic_reduce} & \RAW{LM_IMAGE_SCI_RAW} & \PROD{MASTER_DARK_2RG}, \PROD{MASTER_IMG_FLAT_LAMP_LM}, \PROD{MASTER_IMG_FLAT_TWILIGHT_LM} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI10.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_background} & \RAW{LM_SCI_BASIC_REDUCED}, \RAW{LM_STD_BASIC_REDUCED} &  & \FITS{INS.OPTI10.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_std_process} & \RAW{LM_STD_BKG_SUBTRACTED} & \PROD{FLUXSTD_CATALOG} & \FITS{INS.OPTI10.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_calibrate} & \RAW{LM_SCI_BKG_SUBTRACTED} & \PROD{FLUXCAL_TAB}, \PROD{LM_DISTORTION_TABLE} & \FITS{INS.OPTI10.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_sci_postprocess} & \RAW{LM_SCI_CALIBRATED} &  & \FITS{INS.OPTI10.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_lm_img_distortion} & \RAW{LM_DISTORTION_RAW}, \RAW{LM_WCU_OFF_RAW} & \EXTCALIB{PINHOLE_TABLE} & \FITS{INS.OPTI10.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_n_img_flat} & \RAW{N_FLAT_LAMP_RAW}, \RAW{N_FLAT_TWILIGHT_RAW} & \PROD{MASTER_DARK_GEO} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI10.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_n_img_chopnod} & \RAW{N_IMAGE_SCI_RAW} & \PROD{N_FLAT_LAMP_RAW}, \PROD{N_FLAT_TWILIGHT_RAW} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI10.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_n_img_std_process} & \RAW{N_STD_BKG_SUBTRACTED} & \PROD{FLUXSTD_CATALOG} & \FITS{INS.OPTI13.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_n_img_calibrate} & \RAW{N_SCI_BKG_SUBTRACTED} & \PROD{FLUXCAL_TAB}, \PROD{N_DISTORTION_TABLE} & \FITS{INS.OPTI13.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_n_img_restore} & \RAW{N_SCI_CALIBRATED} &  & \FITS{INS.OPTI13.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_n_img_distortion} & \RAW{N_DISTORTION_RAW}, \RAW{N_WCU_OFF_RAW} & \EXTCALIB{PINHOLE_TABLE} & \FITS{INS.OPTI13.NAME} & \FITS{DRS.FILTER},  \\
\REC{metis_LM_lss_rsrf} & \RAW{LM_LSS_RSRF_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI9.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_trace} & \RAW{LM_LSS_RSRF_PINH_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_LM_LSS_RSRF} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI9.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_wave} & \RAW{LM_LSS_WAVE_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_LM_LSS_RSRF}, \PROD{LM_LSS_TRACE}, \PROD{LASER_TAB} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI9.NAME}, \FITS{SEQ.WCU.LASERn} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT}, \FITS{SEQ.WCU.LASERn},  \\
\REC{metis_LM_lss_std} & \RAW{LM_LSS_STD_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_LM_LSS_RSRF}, \PROD{LM_LSS_DIST_SOL}, \PROD{LM_LSS_WAVE_GUESS}, \PROD{AO_PSF_MODEL}, \PROD{ATM_LINE_CAT}, \PROD{LM_ADC_SLITLOSS}, \PROD{LM_SYNTH_TRANS}, \PROD{REF_STD_CAT} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI9.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_sci} & \RAW{LM_LSS_SCI_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_LM_LSS_RSRF}, \PROD{LM_LSS_DIST_SOL}, \PROD{LM_LSS_WAVE_GUESS}, \PROD{AO_PSF_MODEL}, \PROD{ATM_LINE_CAT}, \PROD{LM_ADC_SLITLOSS}, \PROD{STD_TRANSMISSION}, \PROD{MASTER_LM_RESPONSE} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI9.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_mf_model} & \RAW{LM_LSS_SCI_FLUX_1D} & \PROD{LSF_KERNEL}, \PROD{ATM_PROFILE}, \PROD{ATM_LINE_CAT} & \FITS{INS.OPTI9.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_mf_calctrans} & \RAW{MF_BEST_FIT_TAB} & \PROD{LSF_KERNEL}, \PROD{ATM_PROFILE}, \PROD{ATM_LINE_CAT} & \FITS{INS.OPTI9.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_LM_lss_mf_correct} & \RAW{LM_LSS_SCI_FLUX_1D}, \RAW{LM_LSS_SYNTH_TRANS} &  & \FITS{INS.OPTI9.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_rsrf} & \RAW{N_LSS_RSRF_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI12.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_trace} & \RAW{N_LSS_RSRF_PINH_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO}, \PROD{MASTER_N_LSS_RSRF} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI12.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
%\REC{metis_N_lss_wave} & \RAW{N_LSS_WAVE_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO}, \PROD{MASTER_N_LSS_RSRF}, \PROD{N_LSS_TRACE}, \PROD{LASER_TAB} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI12.NAME}, \FITS{SEQ.WCU.LASERn} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT}, \FITS{SEQ.WCU.LASERn},  \\
\REC{metis_N_lss_std} & \RAW{N_LSS_STD_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO}, \PROD{MASTER_N_LSS_RSRF}, \PROD{N_LSS_DIST_SOL}, \PROD{N_LSS_WAVE_GUESS}, \PROD{AO_PSF_MODEL}, \PROD{ATM_LINE_CAT}, \PROD{N_ADC_SLITLOSS}, \PROD{N_SYNTH_TRANS}, \PROD{REF_STD_CAT} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI12.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_sci} & \RAW{N_LSS_SCI_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO}, \PROD{MASTER_N_LSS_RSRF}, \PROD{N_LSS_DIST_SOL}, \PROD{N_LSS_WAVE_GUESS}, \PROD{AO_PSF_MODEL}, \PROD{ATM_LINE_CAT}, \PROD{N_ADC_SLITLOSS}, \PROD{STD_TRANSMISSION}, \PROD{MASTER_N_RESPONSE} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI12.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_mf_model} & \RAW{N_LSS_SCI_FLUX_1D} & \PROD{LSF_KERNEL}, \PROD{ATM_PROFILE}, \PROD{ATM_LINE_CAT} & \FITS{INS.OPTI12.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_mf_calctrans} & \RAW{MF_BEST_FIT_TAB} & \PROD{LSF_KERNEL}, \PROD{ATM_PROFILE}, \PROD{ATM_LINE_CAT} & \FITS{INS.OPTI12.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_N_lss_mf_correct} & \RAW{N_LSS_SCI_FLUX_1D}, \RAW{N_LSS_SYNTH_TRANS} &  & \FITS{INS.OPTI12.NAME} & \FITS{DRS.SLIT},  \\
\REC{metis_ifu_wavecal} & \RAW{IFU_WAVE_RAW} & \PROD{MASTER_DARK_IFU}, \PROD{IFU_DISTORTION_TABLE} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI6.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.IFU},  \\
\REC{metis_ifu_rsrf} & \RAW{IFU_RSRF_RAW} & \PROD{MASTER_DARK_IFU}, \PROD{IFU_WAVECAL} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI6.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.IFU},  \\
\REC{metis_ifu_calibrate} & \RAW{IFU_STD_RAW} & \PROD{MASTER_DARK_IFU}, \PROD{RSRF_IFU}, \PROD{IFU_WAVECAL}, \PROD{IFU_DISTORTION_TABLE} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI6.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.IFU},  \\
\REC{metis_ifu_telluric} & \RAW{IFU_SCI_COMBINED} & \PROD{LSF_KERNEL}, \PROD{ATM_PROFILE} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI6.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.IFU},  \\
\REC{metis_ifu_calibrate} & \RAW{IFU_SCI_REDUCED}, \PROD{FLUXCAL_TAB} &  & \FITS{INS.OPTI6.NAME} & \FITS{DRS.IFU},  \\
\REC{metis_ifu_postprocess} & \RAW{IFU_SCI_REDUCED} &  & \FITS{INS.OPTI6.NAME} & \FITS{DRS.IFU},  \\
\REC{metis_ifu_distortion} & \RAW{IFU_DISTORTION_RAW} & \EXTCALIB{PINHOLE_TABLE} & \FITS{INS.OPTI6.NAME} & \FITS{DRS.IFU},  \\
\REC{metis_img_adi_cgrph} & \RAW{LM_SCI_BASIC_REDUCED}, \RAW{N_SCI_BKG_SUBTRACTED} & \PROD{LM_DISTORTION_TABLE}, \PROD{N_DISTORTION_TABLE}, \PROD{LM_cgrph_SCI_THROUGHPUT}, \PROD{N_cgrph_SCI_THROUGHPUT} & \FITS{INS.OPTI1.NAME}, \FITS{INS.OPTI3.NAME}, \FITS{INS.OPTI5.NAME}, \FITS{INS.OPTI9.NAME}, \FITS{INS.OPTI10.NAME}, \FITS{INS.OPTI13.NAME} & \FITS{DRS.MASK},  \\
\REC{metis_lm_adi_app} & \RAW{LM_SCI_BASIC_REDUCED} & \PROD{LM_DISTORTION_TABLE}, \PROD{LM_OFF_AXIS_PSF_RAW} & \FITS{INS.OPTI5.NAME}, \FITS{INS.OPTI9.NAME}, \FITS{INS.OPTI10.NAME} & \FITS{DRS.MASK},  \\
\REC{metis_ifu_adi_cgrph} & \RAW{IFU_SCI_REDUCED} & \PROD{IFU_DISTORTION_TABLE}, \PROD{IFU_CGRPH_SCI_THROUGHPUT} & \FITS{INS.OPTI6.NAME}, \FITS{INS.OPTI1.NAME}, \FITS{INS.OPTI3.NAME}, \FITS{INS.OPTI5.NAME}, \FITS{INS.OPTI9.NAME}, \FITS{INS.OPTI12.NAME} & \FITS{DRS.MASK},  \\
\REC{metis_pupil_imaging} & \RAW{LM_PUPIL_RAW}, \RAW{N_PUPIL_RAW} &  & \FITS{INS.OPTI15.NAME}, \FITS{INS.OPTI16.NAME}, \FITS{INS.OPTI10.NAME}, \FITS{INS.OPTI13.NAME} & \FITS{DRS.PUPIL},  \\
\REC{metis_img_chophome} & \RAW{LM_CHOPPERHOME_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_IMG_FLAT_LAMP_LM} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{INS.OPTI10.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_lm_adc_slitloss} & \RAW{LM_SLITLOSSES_RAW}, \RAW{LM_WCU_OFF_RAW} & \PROD{LINEARITY_2RG}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_2RG}, \PROD{MASTER_DARK_2RG}, \PROD{MASTER_IMG_FLAT_LAMP_LM} & \FITS{INS.OPTI10.NAME}, \FITS{INS.OPTI13.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
\REC{metis_n_adc_slitloss} & \RAW{LM_SLITLOSSES_RAW}, \RAW{LM_WCU_OFF_RAW} & \PROD{LINEARITY_GEO}, \PROD{PERSISTENCE_MAP}, \PROD{GAIN_MAP_GEO}, \PROD{MASTER_DARK_GEO}, \PROD{MASTER_IMG_FLAT_LAMP_N} & \FITS{INS.OPTI10.NAME}, \FITS{INS.OPTI13.NAME} & \FITS{DET.DIT}, \FITS{DET.NDIT}, \FITS{DRS.FILTER},  \\
    \hline
    \end{longtable}
  }
\end{landscape}
\restoregeometry

%%% Local Variables:
%%% TeX-master: "METIS_DRLD"
%%% End:
